% Nick Gerakines 2024
% nick_gerakines_resume.tex

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{#1}}%
  \item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{-0.5#1}}%
  \item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
  #1 &
  #2 \\
\end{tabular*}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Nick Gerakines}} (he/him)
\end{center}
\begin{center}
\begin{tabular}{ r@{\hspace{10pt}} c@{\hspace{10pt}} l@{\hspace{10pt}} }
  Dayton, Ohio & \textbullet & \(415\) 963-1165 \\
  nick.gerakines@gmail.com & \textbullet & github.com/ngerakines \\
\end{tabular}
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
  \parskip=0.1em

  \item
  \headerrow
    {\textbf{University Of Dayton Research Institute / Air Force Research Laboratory}}
    {\textbf{Remote | Ohio}}
  \\
  \headerrow
    {\emph{Senior Software Research Engineer}}
    {\emph{May 2023 -- Present}}
  \begin{itemize*}
    \item Designed and implemented networks and systems to support application development, testing, and demonstration. Currently supporting multiple teams of engineers with room to grow.
    \item Implemented AI / ML / CS systems and components to support the cognitively enhanced complex event processing and autonomy mission.
    \item Python, Rust, AI/ML/CS, Kubernetes, Ansible, LLMs, NLP (AMR), Data Warehousing, DevOps, Leadership
  \end{itemize*}

  \item
  \headerrow
    {\textbf{PredictAP}}
    {\textbf{Remote | Massachusetts}}
  \\
  \headerrow
    {\emph{Principal Software Engineer}}
    {\emph{July 2021 -- June 2023}}
  \begin{itemize*}
    \item Implemented the proof of concept that became our core platform including AI/ML/CS prediction engine and SaaS product. Currently supporting hundreds of tenants at thousands of invoices an hour.
    \item Designed, implemented, maintained, and enhanced application platform and underlying AWS infrastructure. Enabled rapid scale up of tenants to new datacenters within minutes.
    \item Worked with leadership to create a sustaining product and was able to grow the team from 2 engineers to 12 engineers over 2 years time without any VC money.
    \item DevOps, Python, AWS, Rust, AI/ML, React, Kubernetes, Terraform, Data Pipelines, Data Warehousing, Leadership
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Datadog}}
    {\textbf{Remote | New York}}
  \\
  \headerrow
    {\emph{Infrastructure Engineer}}
    {\emph{April 2020 -- July 2021}}
  \begin{itemize*}
    \item Designed and implemented replacement for DNS and consul as primary service-discovery mechanism using multi-cluster, multi-cloud, multi-region application and envoy sidecar.
    \item Wrote internal RFCs and actively participated in the review and approval process of initiatives inside and outside of my immediate team.
    \item Responded to incidents and contributed to continuous improvement of our response processes and tools.
    \item Golang, Kubernetes, Consul, AWS, Azure, Google Cloud, Observability
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Mattel}}
    {\textbf{Remote | California | New York}}
  \\
  \headerrow
    {\emph{Principal Software Engineer | Director of Software Engineering}}
    {\emph{May 2017 -- April 2020}}
  \begin{itemize*}
    \item Lead the Mattel Connected Products Platform team to develop IoT initiatives and products.
    \item Scaled the Sproutling organization into a division at Mattel that was responsible for products across major division lines including Barbie, Hot Wheels, Fisher Price, and smaller product divisions.
    \item Worked with multiple functional and cross-functional teams to support existing and create new toy lines. Hot Wheels ID is an example of one product that included the creation of entirely new technologies and manufacturing processes.
    \item Provided consultation across the organization on technical and non-technical solutions to meet business needs. One example was the architecture of identity management systems and the wholistic replacement of mixed legacy authentication across Mattel.
    \item Golang, RPC, OAuth / Identity, Google Cloud, AWS, Game Server Development, iOS, Android, NFC, Hardware/Firmware, Leadership
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Colibri Learning}}
    {\textbf{Pennsylvania | Missouri}}
  \\
  \headerrow
    {\emph{Principal Software Engineer | Director of Engineering}}
    {\emph{September 2014 -- May 2017}}
  \begin{itemize*}
    \item Contributed to and oversaw the technical design and implementation of our product offerings.
    \item Implemented a replacement of legacy .net application stack with modern tooling that lead to 80\% reduction in production infrastructure cost and 10x increase in web application response times.
    \item Hired and managed team of local and remote technical and non-technical staff.
    \item Performed due diligence during acquisitions and was directly responsible for technology and security onboarding of 3 brands during my tenure.
    \item Typescript, Node, AWS, C\#, .Net Core, Docker, Leadership
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Hightail}}
    {\textbf{California}}
  \\
  \headerrow
    {\emph{Staff Engineer}}
    {\emph{May 2013 -- September 2014}}

  \item
  \headerrow
    {\textbf{Blizzard Entertainment}}
    {\textbf{California}}
  \\
  \headerrow
    {\emph{Sr. Software Engineer 2}}
    {\emph{March 2010 -- May 2013}}

  \item
  \headerrow
    {\textbf{Electronic Arts}}
    {\textbf{California}}
  \\
  \headerrow
    {\emph{Platform Architect}}
    {\emph{October 2008 -- February 2010}}

  \item
  \headerrow
    {\textbf{Yahoo! Inc}}
    {\textbf{California}}
  \\
  \headerrow
    {\emph{Software Engineer}}
    {\emph{November 2006 -- October 2008}}

  \item
  \headerrow
    {\textbf{SixApart}}
    {\textbf{California}}
  \\
  \headerrow
    {\emph{Software Engineer}}
    {\emph{January 2006 -- November 2006}}
\end{itemize}

\vspace{-0.4em}
\subsection*{Projects and Personal Experience}

\begin{itemize}
  \parskip=0.1em

  \item
  \headerrow
    {\textbf{Facebook Application: I Play WoW}}
    {\textbf{}}
    I Play WoW is a Facebook application that bridges the two social worlds of Facebook and Blizzard's World of Warcraft. Sold to Electronic Arts in 2009.
  \item
  \headerrow
    {\textbf{Facebook Application Development}}
    {\textbf{ISBN 0470246669}}
    Published in 2008, brought readers through the process of creating and maintaining a Facebook application using all of the features and tools available at the time.
  \item
  \headerrow
    {\textbf{Managing AWS with Terraform}}
    {\textbf{ISBN 9780999799604}}
    Managing AWS with Terraform is a hands-on guide to using Terraform to manage environments in AWS. The focus was on simplicity, security, maintainability, and room for growth to fit future project needs.
  \item
  \headerrow
    {\textbf{Developer Community and Leadership}}
    {\textbf{}}
    Active in software development and technology communities and conferences. Spoke and presented at events including ACM ICFP, Erlang Factory, and language user groups. Organized events, presentations and have contributed to different projects and organizations that do so.
  \item
  \headerrow
    {\textbf{Open Source Contributions}}
    {\textbf{}}
    Active in the open source community through contributions to major open source projects as well as the creation and maintenance of several.
\end{itemize}

\vspace{-0.4em}
\subsection*{Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
Technical
\begin{itemize*}
  \item 10+ years of DevOps experience
  \item 10+ years of MySQL, Postgres
  \item 10+ years of Linux administration, configuration and usage
  \item 7+ years of Golang, Python
  \item 6+ years of AWS (conosole, API, libraries)
  \item 5+ years of Erlang, Java, C, C++, Perl
  \item 4+ years of NodeJS, JavaScript, Rust, Ruby, C\#, Obj-C
  \item GCP, Unity, AR / VR, ActivityPub, OAuth, PKI, Intellectually Property Rights, and more protocols than I can list here.
\end{itemize*}

\end{indentsection}

\end{document}
