% Nick Gerakines 2015
% nick_gerakines_resume.tex

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{#1}}%
  \item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{-0.5#1}}%
  \item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
  #1 &
  #2 \\
\end{tabular*}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Nick Gerakines}}
\end{center}
\begin{center}
\begin{tabular}{ r@{\hspace{10pt}} c@{\hspace{10pt}} l@{\hspace{10pt}} }
  Dayton, Ohio & \textbullet & \(415\) 963-1165 \\
  nick.gerakines@gmail.com & \textbullet & github.com/ngerakines \\
\end{tabular}
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
  \parskip=0.1em

  \item
  \headerrow
    {\textbf{GitHub Copilot}}
    {\textbf{Remote | Ohio}}
  \\
  \headerrow
    {\emph{Senior Software Engineer}}
    {\emph{March 2024 -- Present}}
  \begin{itemize*}
    \item Contributed to the release of GitHub Copilot model integrations including Open AI GPT 4, 4o, 4.5, o1, and o3, Claude 3.5 and 3.7 Sonnet, Gemini 1.5 and 2.0, and variants.
    \item Developed infrastraucture and tooling to support the release of the Copilot Chat product including the integration of the Copilot Chat product into the GitHub platform.
    \item Supported the product through incident response and triage, including the development of observability process and tooling to support the incident response process.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{University Of Dayton Research Institute / Air Force Research Laboratory}}
    {\textbf{Remote | Ohio}}
  \\
  \headerrow
    {\emph{Senior Software Research Engineer}}
    {\emph{May 2023 -- March 2024}}
  \begin{itemize*}
    \item I designed and implemented network infrastructure, hardware provisioning, and virtual device provisioning using ansible and Kubernetes (k3s.io) on on-prem hardware including bespoke, purpose hardware provided by the Air Force. These networks support the full lifecycle of development, testing, and demonstration. Currently supporting multiple teams of engineers with room to grow.
    \item Implemented AI / ML / CS training, execution, library, and API daemons and processes that ran on custom and commodity hardware to support the cognitively enhanced complex event processing and autonomy mission. This included complex natural language processing and retrieval-augmented generation.
    \item Created job scheduling tools in Python and Rust for bare metal, virtual machine, and distributed system container orchestration and management.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{PredictAP}}
    {\textbf{Remote | Massachusetts}}
  \\
  \headerrow
    {\emph{Principal Software Engineer}}
    {\emph{July 2021 -- June 2023}}
  \begin{itemize*}
    \item Implemented the proof of concept that became our core platform including AI/ML prediction engine and SaaS product using Python. Currently supporting hundreds of tenants at thousands of invoices an hour.
    \item Designed, implemented, maintained, and enhanced application platform and underlying AWS infrastructure using Kubernetes and Terraform. Enabled rapid scale up of tenants to new datacenters within minutes.
    \item As engineer \#1, I worked with leadership to produce a profitable product and use its success to expand the engineering organization.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Datadog}}
    {\textbf{Remote | New York}}
  \\
  \headerrow
    {\emph{Infrastructure Engineer}}
    {\emph{April 2020 -- July 2021}}
  \begin{itemize*}
    \item Designed and implemented replacement for DNS and Consul as primary service-discovery mechanism using multi-cluster, multi-cloud, multi-region Kubernetes operators in Go with envoy sidecars.
    \item Wrote internal RFCs and actively participated in the review and approval process of initiatives inside and outside of my immediate team.
    \item Responded to incidents and contributed to continuous improvement of our response processes and tools.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Mattel}}
    {\textbf{Remote | California | New York}}
  \\
  \headerrow
    {\emph{Principal Software Engineer | Director of Software Engineering}}
    {\emph{May 2017 -- April 2020}}
  \begin{itemize*}
    \item Scaled the Sproutling organization into the Mattel Connected Products Platform division within Mattel that was responsible for products across major organization lines including Barbie, Hot Wheels, and Fisher Price.
    \item Worked with multiple functional and cross-functional teams to support existing and create new toy lines. Hot Wheels ID is an example of one product that included the creation of entirely new technologies and manufacturing processes.
    \item Provided consultation across the organization on technical and non-technical solutions to meet business needs. One example was the architecture of identity management systems and the wholistic replacement of mixed legacy authentication across Mattel.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Colibri Learning}}
    {\textbf{Pennsylvania | Missouri}}
  \\
  \headerrow
    {\emph{Principal Software Engineer | Director of Engineering}}
    {\emph{September 2014 -- May 2017}}
  \begin{itemize*}
    \item Implemented a replacement of legacy .net application stack with modern tooling that lead to 80\% reduction in production infrastructure cost and 10x increase in web application response times.
    \item Hired and managed team of local and remote technical and non-technical staff including .Net, Node, and Angular teams as well as technical writing.
    \item Performed due diligence during acquisitions and was directly responsible for technology and security onboarding of 3 brands during my tenure.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Hightail}}
    {\textbf{California}}
  \\
  \headerrow
    {\emph{Staff Engineer}}
    {\emph{May 2013 -- September 2014}}
  \begin{itemize*}
    \item Senior member of the engineering team responsible for building applications, services and libraries to enhance the value of and increase business.
    \item Worked with team members to create a document preview image rendering farm.
    \item Worked with team members to create Hightail search service.
  \end{itemize*}


  \item
  \headerrow
    {\textbf{Blizzard Entertainment}}
    {\textbf{California}}
  \\
  \headerrow
    {\emph{Sr. Software Engineer 2}}
    {\emph{March 2010 -- May 2013}}
  \begin{itemize*}
    \item Senior member of the engineer team responsible for designing, implementing and delegating work for internal and external projects and initiatives.
    \item Work with directors and leads to document and enforce team standards and practices.
    \item Lead the development and release of World of Warcraft and Diablo 3 Web APIs.
    \item Designed, created and oversaw the hand off of the search system used across all of our community sites as well as a distributed image rendering farm that powers the World of Warcraft game site.
    \item Owned and was responsible for a variety of libraries, tools and developer toolkits used to create and manage our web application stack.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Electronic Arts}}
    {\textbf{California}}
  \\
  \headerrow
    {\emph{Platform Architect}}
    {\emph{October 2008 -- February 2010}}
  \begin{itemize*}
    \item Built out the Rupture Platform team and bootstrapped the technologies used by that team.
    \item Oversaw the training and growth of team members new to the Erlang programming language and helped set and re-enforce standards and practices used by the team.
    \item Oversaw game team integration and relationship development with Rupture.
    \item Lead the development and release of the Rupture API and various components of the API.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Yahoo! Inc}}
    {\textbf{California}}
  \\
  \headerrow
    {\emph{Software Engineer}}
    {\emph{November 2006 -- October 2008}}
  \begin{itemize*}
    \item Designed and helped implement the internal del.icio.us API.
    \item Worked on TagWeb, a federated data-store over Apache and MySQL.
    \item Worked closely with the front-end and back-end teams to design and implement the communication protocols between the systems and also wrote extensive test suite to cover the protocols.
    \item Designed and implemented secondary systems used by delicious including spam and abuse detection.
    \item Worked on Yahoo! Mobile iOS applications.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{SixApart}}
    {\textbf{California}}
  \\
  \headerrow
    {\emph{Software Engineer}}
    {\emph{January 2006 -- November 2006}}
  \begin{itemize*}
    \item Contributed to the TypePad blogging service.
    \item Contributed to several notable open source projects including Memcached, Perlbal, and MogileFS.
    \item Released the TypePad Mobile project and TypePad APIs (Atom).
  \end{itemize*}
\end{itemize}

\vspace{-0.4em}
\subsection*{Projects and Personal Experience}

\begin{itemize}
  \parskip=0.1em

  \item
  \headerrow
    {\textbf{Facebook Application: I Play WoW}}
    {\textbf{}}
    I Play WoW is a Facebook application that bridges the two social worlds of Facebook and Blizzard's World of Warcraft. The application was originally written in Perl over Catalyst with Memcached and MySQL. As the application started to grow parts of it were moved to Erlang and CouchDB. Sold to Electronic Arts in 2009.
  \item
  \headerrow
    {\textbf{Facebook Application Development}}
    {\textbf{ISBN 0470246669}}
    Published in 2008, my first book brought readers through the process of creating and maintaining a Facebook application using all of the features and tools available at the time.
  \item
  \headerrow
    {\textbf{Managing AWS with Terraform}}
    {\textbf{ISBN 9780999799604}}
    Managing AWS with Terraform is a hands-on guide to using Terraform to manage environments in AWS. We focus on simplicity, security, and maintainability, giving you everything you need to get started and make progress as you work through it.
  \item
  \headerrow
    {\textbf{Developer Community Participation}}
    {\textbf{}}
    Active in various software development communities and conferences. Have spoken and presented at conferences and gatherings including ACM ICFP, Erlang Factory and language user groups. Have actively organized events, presentations and have contributed to different projects and organizations that do so.
  \item
  \headerrow
    {\textbf{Open Source Contributions}}
    {\textbf{}}
    Active in the open source community through contributions to major open source projects as well as the creation and maintenance of several.
\end{itemize}

\vspace{-0.4em}
\subsection*{Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
Technical
\begin{itemize*}
  \item 9+ years of DevOps experience
  \item 6+ years of Golang development
  \item 5+ years of Erlang, Java, C/C++, and Perl development
  \item 4+ years of NodeJS/JavaScript development
  \item 3+ years of Rust, Ruby, C\#, Objective-c/Cocoa development
  \item 8+ years of MySQL / Postgres administration and usage
  \item 10+ years of Linux administration, configuration and usage
  \item 5+ years of AWS administration and usage
  \item 3+ years of GCP and Oracle administration and usage
  \item 1 year of Unity / VR application development
  \item 10+ years of REST / RPC design and implementation
  \item ActivityPub, OAuth, PKI, Intellectually Property Rights, and more protocols than I can list here.
\end{itemize*}

\end{indentsection}

\end{document}
